\documentclass{res} % Use the custom res.cls style

\usepackage{hyperref}
\usepackage{amssymb} % For \nearrow

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Kashif Ahmad} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 97098 13874 \\ Kolkata, India} 
\address{\href{mailto:kash151if@gmail.com}{kash151if@gmail.com} \\ \href{https://www.linkedin.com/in/kashif-ahmad-373286164}{LinkedIn} \\ \href{https://auth.geeksforgeeks.org/user/kash15if/practice}{GeeksForGeeks} \\ \href{https://github.com/Kash15if}{GitHub}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

% \begin{rSection}{OBJECTIVE}

% {Software Engineer with 2 years of experience in JavaScript, SQL and backend technologies, seeking full-time Software Engineering roles.}

% \end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------


\begin{rSection}{WORK EXPERIENCE}

\textbf{Software Developer} \hfill Jul 2022 - Present\\
Greenwave Solutions Pvt. Ltd. \hfill \textit{Kolkata, India}
 \begin{itemize}
    \itemsep -5pt {} 
    \item Led an internal employee service portal for company employees, featuring leave management, claims processing, notifications, and access to salary slips. All senstive values are encypted.
     \item Led the development and redevelopment of multiple modules in the Digital Logbooks and Workflow, which is the product of our company.
     \item Dockerized multiple monolithic applications and microservices to simplify their deployment, enhance customizability, and enable easy deployment.
     \item Implemented a user authentication and security module that eliminated 100 percent paper logbook usage and enabled sequential workflow of multiple jobs in the industry.
     \item Configured encrypted database credentials inside the property files using node.js API.
     \item Developed a Java application for multiple clients to transfer data between PostgreSQL, 
MS SQL, MySQL, OracleDB and MongoDB databases. The application was integrated with a scheduler to 
automate the data transfer process at regular intervals.

    \item Tech stack in use: React.js, Node.js, Redux, Java, JSF, SQL, Docker, jwt, bcrypt.
 \end{itemize}
 
\textbf{Associate Software Engineer} \hfill Jul 2021 - Jun 2022\\
Greenwave Solutions Pvt. Ltd. \hfill \textit{Kolkata, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Led the transformation of a large JSF monolith to microservices using React and Spring Boot
    and implemented real-time data visualization with web socket integration.
\item Utilized JavaScript's event loop concept to optimize page load time.
and by breaking down each component of the page into separate responsibilities, page load time was reduced by around 50 percent (up to 90 percent for larger datasets).

    \item Created robust APIs in Node.js for end-to-end data transfer and client-facing REST APIs for seamless interaction with the products.
     \item Developed the backend for a PTC Thingworx platform for a client.
   
    \item Tech stack used:  React.js, Node.js, Redux, Graphql, TypeScript, JavaScript, MsSQL, PostgreSQL , MongoDB, MySQL Socket.IO, Java, Chart.js, Express.js, JSF, HTML, CSS, Mui.
 \end{itemize}

\textbf{Database Engineering Intern} \hfill Apr 2021 - Jun 2021\\
Greenwave Solutions Pvt. Ltd. \hfill \textit{Kolkata, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Worked as an SQL developer.
     \item Improved reporting rates by developing dashboard and reporting system on PTC Thingworx.
    \item Tech stack used: JavaScript, SQL, PTC Thingworx
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B. Tech. in Computer Science}, University of Calcutta \hfill {June 2021}

\end{rSection}

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & JavaScript, Java, HTML, CSS
\\
Frameworks and Libraries & Node.js, Express.js, React, React.native, Vue, Mui, Spring, SpringBoot JSF-Primefaces, Flutter, PrimefaceReact, Bootstrap, Chart.js.
\\
Database & SQL, MS SQL, PostgreSQL, PL/PGSQL, MongoDB, Firebase
\\
Other Technologies & Git, GitHub, VS Code, Socket.IO, Docker, PTC Thingworx
\\
\end{tabular}\\
\end{rSection}




%----------------------------------------------------------------------------------------
%	Personal Project SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PERSONAL PROJECTS}
\vspace{-1.25em}



% This is a link with the \(\nearrow\) symbol: \href{https://www.example.com}{\texorpdfstring{\(\nearrow\)}{nearrow}}



\item \textbf{Custom Components}
\href{https://custom-components-orpin.vercel.app/}text{Up arrow}{\texorpdfstring{\(\nearrow\)}{nearrow}}
{A collection of custom React components that are frequently used but were not readily available or easily customizable. The components include dynamic and responsive tables with features such as sorting, filtering, CRUD operations, Excel upload and download, dynamic and responsive carousels or sliders with a 3D view using the concept of CSS clip path, pop-ups, cards, multi-checkbox selection, alerts, collapsible elements, etc. Each component is fully customizable to suit the design needs of any project. I am planning to expand it further and add features like diagrams, organization charts, etc.}



\item \textbf{Meal Booking System}
\href{https://meal-booking-system.vercel.app/}{\texorpdfstring{\(\nearrow\)}{nearrow}}
{
The responsive full-stack web application is designed for advanced meal booking in hostels, offices, or commercial spaces. It offers a range of features, including the ability for users to book meals for the next seven days, track their meal records, view billing information, and access an intuitive dashboard. Administrators have access to a separate section with functionalities such as managing meals, expenses, and user details, as well as generating bills and reports. The application aims to provide a seamless experience for users and efficient management tools for administrators. They can also generate bills and reports, including the ability to mail bills to users with a single click. Additionally, administrators can conveniently download Excel files containing both summary and individual user data.}





\item \textbf{Online Exam Portal}
\href{https://react-online-exam-portal.vercel.app/}{\texorpdfstring{\(\nearrow\)}{nearrow}}
{
This is an online exam portal provides users with the ability to take exams conveniently. The platform allows administrators to add questions using Excel, ensuring efficient question management. Additionally, the portal includes a feature that tracks user activities, enabling administrators to monitor user behavior, such as tab switching or any other actions. This tracking feature provides administrators with valuable insights and helps maintain exam integrity.}




            
\item \textbf{Flat Expense Records (Split App)}
\href{https://github.com/Kash15if/react-flat-expense-record}{\texorpdfstring{\(\nearrow\)}{nearrow}}
{A React-based expense tracker with Firebase backend, similar to Split app. It features dark and light mode options, allowing users to manage expenses, track multiple users, and generate insightful reports.}



\item \textbf{Study Planner} 
\href{https://study-planner-phi.vercel.app/dashboard}{\texorpdfstring{\(\nearrow\)}{nearrow}}
{A Full Stack responsive web app for organized schedule outlining study times and learning goals containing dashboard and multiple charts. User will receive warning mail before the deadline. Build using HTMl, CSS, Mui and Redux for Front End and node.js, Express.js for Back End and for DataBase PostgresSQL is used. For scheduled task and Email Node Mailer and Node Schedule is used here}


\item {\bf Grocery List Builder}
\href{https://react-grocery-list-firebase.vercel.app/}{\texorpdfstring{\(\nearrow\)}{nearrow}}  {A React-based expense tracker with Firebase backend, similar to Split app. It features dark and light mode options, allowing users to manage expenses, track multiple users, and generate insightful reports..}


\item {\bf Snake and Ladder}
\href{https://vue-snake-ladder.vercel.app/}{\texorpdfstring{\(\nearrow\)}{nearrow}}
{A Full Stack real time muiltiplayer snake and ladder game built using HTML, CSS and Vue.js for Front End and Firebase Firestore for realtime database}

 
\item \textbf{Covid-19 tracker} 
\href{https://covid19status.vercel.app/}{\texorpdfstring{\(\nearrow\)}{nearrow}}
{A responsive web-app made in Vue.js with HTML, CSS, Bootstrap as front-end, used library such as Map-box GL,
			Chart.js also used Covid19India and covid19 API for real-time
			data.}


\item \textbf{Portfolio}
\href{https://portfolio.kashif.world/}{\texorpdfstring{\(\nearrow\)}{nearrow}}
{My portfolio website built in Bootstrap, Hyml, CSS}



\item {\bf All Projects}
\href{https://myprojects.vercel.app/}{\texorpdfstring{\(\nearrow\)}{nearrow}}  {All Projects is being shown in the cards using github public API.}
\item 

\end{rSection}


\end{document}